Verifying Demonstrations

### 2021-06-16 paper/P-signatures.tex
Changes "i.e.\ " and "e.g.\ " to \ie and \eg
More workaround: wrap sub- and superscripts in {}

\NewCryptoScheme{\Psig}{Psig}

@@

\NewCryptoFunction{\PSetup}{\Psig.\!Setup}

\(params\gets \PSetup[1^\lambda]\): generates the global parameters \(params\), 
which contains parameters for the underlying algorithms.
For ease of notation we will omit \(params\) from all functions.

\NewCryptoFunction{\PCommit}{\Psig.\!Commit}

\(comm\gets \PCommit[m, open]\): takes a message \(m\) and an opening value 
\(open\) and returns a commitment.
The commitment scheme must be \emph{perfectly binding} and \emph{strongly 
  computationally hiding}.
Perfectly binding means that for every bit string \(comm\) there exists at most 
one value \(x\) such that there exists a value \(open\) with \(comm = 
  \PCommit[x, open]\).
Strongly computationally hiding means that there exists an alternate setup 
algorithm which generates indistinguishable parameters which yields 
information-theoretically hiding commitments.
I.e.\ the adversary cannot tell which setup algorithm has been used.

\NewCryptoFunction{\PObtainSig}{\Psig.\!ObtainSig}
\NewCryptoFunction{\PIssueSig}{\Psig.\!IssueSig}

@@

\NewCryptoFunction{\PProve}{\Psig.\!Prove}

@@

\NewCryptoFunction{\PVerifyProof}{\Psig.\!VerifyProof}

@@

\NewCryptoFunction{\PEqCommProve}{\Psig.\!EqCommProve}

@@

\NewCryptoFunction{\PVerEqComm}{\Psig.\!VerEqComm}

>>>>

@@

\(params\gets \PSetup[1^{\lambda}]\): generates the global parameters \(params\), 
which contains parameters for the underlying algorithms.
For ease of notation we will omit \(params\) from all functions.

\(comm\gets \PCommit[m, open]\): takes a message \(m\) and an opening value 
\(open\) and returns a commitment.
The commitment scheme must be \emph{perfectly binding} and \emph{strongly 
  computationally hiding}.
Perfectly binding means that for every bit string \(comm\) there exists at most 
one value \(x\) such that there exists a value \(open\) with \(comm = 
  \PCommit[x, open]\).
Strongly computationally hiding means that there exists an alternate setup 
algorithm which generates indistinguishable parameters which yields 
information-theoretically hiding commitments.
\Ie the adversary cannot tell which setup algorithm has been used.

@@

@@

@@

@@

### 2021-06-16 paper/ZKPK-instantiations.tex
More workaround: wrap sub- and superscripts in {}

For the convenience of the reader, we summarize 
(from~\cite{Camenisch-phdthesis}) how to instantiate general \acp{ZKPK} for 
discrete logarithms based on the Schnorr identification scheme~\cite{Schnorr}, 
which, in its original form, can be written as \(\PK[\alpha][A = g^\alpha]\).
The generalized form would be \(\PK[\alpha_1, \dotsc, \alpha_n][A = 
    \prod_{i=1}^n g_i^{\alpha_i}]\).
This could equivalently be written as
\begin{equation*}
  \Proto%
  {\PKprove[\{g_i\}_i, q, A, \{\alpha_i\}_i]}%
  {\PKverify[\{g_i\}_i, q, A]},
\end{equation*}
where \(\PKprove\) is run by the prover and \(\PKverify\) is run by the 
verifier.
\(\PKverify\) outputs accept (\(\top\)) or reject (\(\bot\)).
We give an instance of \(\PKprove\) and \(\PKverify\) in \cref{PKalgorithms}.
We also note that
\begin{multline*}
  \PK[\alpha, \beta][A = g^\alpha \land B = g^\beta] = \\
  \PK[\alpha][A = g^\alpha] \land \PK[\beta][B = g^\beta],
\end{multline*}
however, the challenge \(c\) must be the same in both sub-protocols.

\begin{figure*}
  %\centering
  \small
  \begin{tabular}{lcl}
    \(\PKprove[\{g_i\}_{i=1}^n, q, \{\alpha_i\}_{i=1}^n]\):
    &
    & \(\PKverify[\{g_i\}_{i=1}^n, q, A]\):
    \\
    \midrule

@@

  \end{tabular}
  \caption{%
    \(\PK[\alpha_1, \dotsc, \alpha_n][A = \prod_{i=1}^n g_i^{\alpha_i}]\) using 
    the Schnorr identification scheme~\cite{Camenisch-phdthesis}.
  }%
  \label{PKalgorithms}
\end{figure*}

@@

For the non-interactive instance, \(\SPK[\alpha][A = g^\alpha][m]\), we use the 
Fiat-Shamir heuristic~\cite{FiatShamirHeuristic} on the above protocol, 
illustrated as \(\SPKprove\) and \(\SPKverify\) in \cref{SPKalgorithms}.

@@

  \begin{algorithmic}
    \Function{$\SPKverify$}{$\{g_i\}_i, q, A, m, \{s_i\}_i, c$}
      \State{$\hat R \gets A^c \prod_{i=1}^n g_i^{s_i}$}
      \If{$c = H(\{g_i\}_i\concat A\concat \hat R\concat m)$}
        \State{\Return{$\top$}}
      \EndIf{}
      \State{\Return{$\bot$}}
    \EndFunction{}
  \end{algorithmic}
  \caption{%
    \(\SPK[\alpha_1, \dotsc, \alpha_n][A = \prod_{i=1}^n g_i^{\alpha_i}][m]\) 
    using the Fiat-Shamir heuristic on the Schnorr identification 
    scheme~\cite{Camenisch-phdthesis}.
  }%
  \label{SPKalgorithms}
\end{figure}

>>>>

For the convenience of the reader, we summarize 
(from~\cite{Camenisch-phdthesis}) how to instantiate general \acp{ZKPK} for 
discrete logarithms based on the Schnorr identification scheme~\cite{Schnorr}, 
which, in its original form, can be written as \(\PK[\alpha][A = g^{\alpha}]\).
The generalized form would be \(\PK[\alpha_1, \dotsc, \alpha_n][A = 
    \prod_{i=1}^n g_i^{\alpha_i}]\).
This could equivalently be written as
\begin{equation*}
  \Proto%
  {\PKprove[\{g_i\}_i, q, A, \{\alpha_i\}_i]}%
  {\PKverify[\{g_i\}_i, q, A]},
\end{equation*}
where \(\PKprove\) is run by the prover and \(\PKverify\) is run by the 
verifier.
\(\PKverify\) outputs accept (\(\top\)) or reject (\(\bot\)).
We give an instance of \(\PKprove\) and \(\PKverify\) in \cref{PKalgorithms}.
We also note that
\begin{multline*}
  \PK[\alpha, \beta][A = g^{\alpha} \land B = g^{\beta}] = \\
  \PK[\alpha][A = g^{\alpha}] \land \PK[\beta][B = g^{\beta}],
\end{multline*}
however, the challenge \(c\) must be the same in both sub-protocols.

\begin{figure*}
  %\centering
  \small
  \begin{tabular}{lcl}
    \(\PKprove[\{g_i\}_{i=1}^n, q, A, \{\alpha_i\}_{i=1}^n]\):
    &
    & \(\PKverify[\{g_i\}_{i=1}^n, q, A]\):
    \\
    \midrule

@@

  \end{tabular}
  \caption{%
    \(\PK[\alpha_1, \dotsc, \alpha_n][A = \prod_{i=1}^n g_i^{\alpha_i}]\) using 
    the Schnorr identification scheme.
  }%
  \label{PKalgorithms}
\end{figure*}

@@

For the non-interactive instance, \(\SPK[\alpha][A = g^{\alpha}][m]\), we use the 
Fiat-Shamir heuristic~\cite{FiatShamirHeuristic} on the above protocol, 
illustrated as \(\SPKprove\) and \(\SPKverify\) in \cref{SPKalgorithms}.

@@

  \begin{algorithmic}
    \Function{$\SPKverify$}{$\{g_i\}_i, q, A, m, \{s_i\}_i, c$}
      \State{$\hat R \gets A^c \prod_{i=1}^n g_i^{s_i}$}
      \If{$c = H(\{g_i\}_i\concat A\concat \hat R\concat m)$}
        \State{\Return{$\top$}}
      \EndIf{}
      \State{\Return{$\bot$}}
    \EndFunction{}
  \end{algorithmic}
  \caption{%
    \(\SPK[\alpha_1, \dotsc, \alpha_n][A = \prod_{i=1}^n g_i^{\alpha_i}][m]\) 
    using the Fiat-Shamir heuristic on the Schnorr identification scheme.
  }%
  \label{SPKalgorithms}
\end{figure}

### 2021-06-16 paper/ZKPK.tex
Moves ZKPK instantiations to the appendix
More workaround: wrap sub- and superscripts in {}

We will use the notation introduced by \citet{PKnotation}:
\begin{equation}\label{PKexample}
  \PK[\alpha, \beta, \gamma][y = g^\alpha h^\beta \land y' = \hat g^\gamma],
\end{equation}
which means that we prove knowledge of \(\alpha, \beta, \gamma\) ensuring that \(y, y'\) are of the form \(y = g^\alpha h^\beta\) and \(y' = \hat g^\gamma\), respectively.
Greek letters are known only to the prover and used for the information for which the prover wishes to prove knowledge, while all other letters are known by the verifier.

When a proof of knowledge is turned into a signature using the Fiat-Shamir heuristic~\cite{FiatShamirHeuristic}, we will denote it as
\begin{equation*}\label{SPKexample}
  \sigma\gets \SPK[\alpha, \beta, \gamma]%
  [y = g^\alpha h^\beta \land y' = \hat g^\gamma]%
  [m],
\end{equation*}
which yields a signature \(\sigma\) on \(m\), ensuring that the issuer knows \(\alpha, \beta, \gamma\) such that \(y = g^\alpha h^\beta\) and \(y' = \hat{g}^\gamma\).

>>>>

We will use the notation introduced by \citet{PKnotation}:
\begin{equation}\label{PKexample}
  \PK[\alpha, \beta, \gamma][y = g^{\alpha} h^{\beta} \land y' = \hat g^{\gamma}],
\end{equation}
which means that we prove knowledge of \(\alpha, \beta, \gamma\) ensuring that \(y, y'\) are of the form \(y = g^{\alpha} h^{\beta}\) and \(y' = \hat g^{\gamma}\), respectively.
Greek letters are known only to the prover and used for the information for which the prover wishes to prove knowledge, while all other letters are known by the verifier.

When a proof of knowledge is turned into a signature using the Fiat-Shamir heuristic~\cite{FiatShamirHeuristic}, we will denote it as
\begin{equation*}\label{SPKexample}
  \sigma\gets \SPK[\alpha, \beta, \gamma]%
  [y = g^{\alpha} h^{\beta} \land y' = \hat g^{\gamma}]%
  [m],
\end{equation*}
which yields a signature \(\sigma\) on \(m\), ensuring that the issuer knows \(\alpha, \beta, \gamma\) such that \(y = g^{\alpha} h^{\beta}\) and \(y' = \hat{g}^{\gamma}\).
